<h1>A list a functions to fit data to probability distributions</h1>

<p><strong>Authors:</strong> <a href="mailto:fbaffie@gmail.com">Florian Kobierska Baffie</a> [aut, cre]</p>
<p><strong>Version:</strong> 0.1</p>
<p><strong>License:</strong> MIT</p>

<h4>Description</h4>
<p>This package was developed for the FlomKart project.
It contains functions to fit probability distributions to flood data.
The following distributions are implemented:
- Generalized extreme value (gev)
- Generalized logistics (gl)
- Gumbel (gumbel)
- Gamma (gamma)
- Pearson III (pearson)
Four parameter estimation methods are available:
- Maximum likelihood (mle)
- Linear moments (Lmom)
- Ordinary moments (mom)
- Bayesian inference (bayes)
All functions are named distr_method (i.e. gl_bayes)</p>



<h4>Imports</h4>
<p>
evd,
ismev,
pracma,
nsRFA,
MASS,
fitdistrplus,
plyr</p>

<h4>Suggests</h4>
<p>
testthat,
packagedocs</p>



  ```{r packagedocs_load_library, echo=FALSE}
  suppressWarnings(suppressMessages(
    library(fitdistrib,
      quietly = TRUE, warn.conflicts = FALSE, verbose = FALSE
    )
  ))
  ```
  

# Package Functions





## gamma_bayes

<a id="gamma_bayes_alias"></a><h3>Fitting the gamma distribution with Bayesian inference</h3>

<p class="rd-p">Function to fit the gamma distribution with bayes method
This is a dummy function because this method has not been implemented yet</p>

<h4>Usage</h4>
<pre class="r"><code><div>gamma_bayes(dat)</div></code></pre>

<h4>Arguments</h4>
<dl class="rd-dl">
  <dt>dat</dt>
  <dd class="rd-dd">the data that needs fitting (i.e. flood data)</dd>
</dl>

  <h4>Value</h4>

  <p class="rd-p"><dl>
param Estimated parameters and standard error returned as a list($estimate, $se)
</dl></p>








## gamma_Lmom

<a id="gamma_Lmom_alias"></a><h3>Fitting the gamma distribution with Lmom</h3>

<p class="rd-p">Function to fit the gamma distribution with the linear moment method</p>

<h4>Usage</h4>
<pre class="r"><code><div>gamma_Lmom(dat)</div></code></pre>

<h4>Arguments</h4>
<dl class="rd-dl">
  <dt>dat</dt>
  <dd class="rd-dd">the data that needs fitting (i.e. flood data)</dd>
</dl>

  <h4>Value</h4>

  <p class="rd-p"><dl>
param Estimated parameters (2) and standard error returned as a list($estimate, $se)
</dl></p>



<h4>Examples</h4>
```{r gamma_Lmom_id_2, eval = TRUE }
library(FlomKart)
estimate = gamma_Lmom(test_data)
plot_density(test_data, param = estimate, distr = "gamma")

```





## gamma_mle

<a id="gamma_mle_alias"></a><h3>Fitting the gamma distribution with MLE</h3>

<p class="rd-p">Function to fit the gamma distribution with the maximum likelihood method</p>

<h4>Usage</h4>
<pre class="r"><code><div>gamma_mle(dat)</div></code></pre>

<h4>Arguments</h4>
<dl class="rd-dl">
  <dt>dat</dt>
  <dd class="rd-dd">the data that needs fitting (i.e. flood data)</dd>
</dl>

  <h4>Value</h4>

  <p class="rd-p"><dl>
param Estimated parameters (2) and standard error returned as a list($estimate, $se)
</dl></p>



<h4>Examples</h4>
```{r gamma_mle_id_3, eval = TRUE }
library(FlomKart)
estimate = gamma_mle(test_data)
plot_density(test_data, param = estimate, distr = "gamma")

```





## gamma_mom

<a id="gamma_mom_alias"></a><h3>Fitting the gamma distribution with mom</h3>

<p class="rd-p">Function to fit the gamma distribution with the ordinary moments method</p>

<h4>Usage</h4>
<pre class="r"><code><div>gamma_mom(dat)</div></code></pre>

<h4>Arguments</h4>
<dl class="rd-dl">
  <dt>dat</dt>
  <dd class="rd-dd">the data that needs fitting (i.e. flood data)</dd>
</dl>

  <h4>Value</h4>

  <p class="rd-p"><dl>
param Estimated parameters (2) and standard error returned as a list($estimate, $se)
</dl></p>



<h4>Examples</h4>
```{r gamma_mom_id_4, eval = TRUE }
library(FlomKart)
estimate = gamma_mom(test_data)
plot_density(test_data, param = estimate, distr = "gamma")

```





## get_posterior_gev

<a id="get_posterior_gev_alias"></a><h3>Calculating the posterior predictive distribution</h3>

<p class="rd-p">Function to calculate the posterior predictive distribution after calling gev_bayes</p>

<h4>Usage</h4>
<pre class="r"><code><div>get_posterior_gev(mmrp, mupars, spars, kpars)</div></code></pre>

<h4>Arguments</h4>
<dl class="rd-dl">
  <dt>(mmrp, </dt>
  <dd class="rd-dd">mupars, spars, kpars) parameters returned by gev_bayes. mupars, spars, kpars are the ensemble of param$estimate</dd>
</dl>

  <h4>Value</h4>

  <p class="rd-p"><dl>
param Estimated parameters and standard error returned as a list($estimate, $se)
</dl></p>








## get_posterior_gl

<a id="get_posterior_gl_alias"></a><h3>Calculating the posterior predictive distribution for GL</h3>

<p class="rd-p">Function to calculate the posterior predictive distribution after calling gev_bayes</p>

<h4>Usage</h4>
<pre class="r"><code><div>get_posterior_gl(mmrp, mupars, spars, kpars)</div></code></pre>

<h4>Arguments</h4>
<dl class="rd-dl">
  <dt>(mmrp, </dt>
  <dd class="rd-dd">mupars, spars, kpars) parameters returned by gev_bayes. mupars, spars, kpars are the ensemble of param$estimate</dd>
</dl>

  <h4>Value</h4>

  <p class="rd-p"><dl>
param Estimated parameters and standard error returned as a list($estimate, $se)
</dl></p>








## get_posterior_gumbel

<a id="get_posterior_gumbel_alias"></a><h3>Calculating the posterior predictive distribution</h3>

<p class="rd-p">Function to calculate the posterior predictive distribution after calling gumbel_bayes</p>

<h4>Usage</h4>
<pre class="r"><code><div>get_posterior_gumbel(mmrp, mupars, spars)</div></code></pre>

<h4>Arguments</h4>
<dl class="rd-dl">
  <dt>(mmrp, </dt>
  <dd class="rd-dd">mupars, spars) parameters returned by gumbel_bayes. mupars, spars are the ensemble of param$estimate</dd>
</dl>

  <h4>Value</h4>

  <p class="rd-p"><dl>
param Estimated parameters and standard error returned as a list($estimate, $se)
</dl></p>








## get_posterior_PEARSON

<a id="get_posterior_PEARSON_alias"></a><h3>Calculating the posterior predictive distribution</h3>

<p class="rd-p">Function to calculate the posterior predictive distribution after calling pearson_bayes</p>

<h4>Usage</h4>
<pre class="r"><code><div>get_posterior_PEARSON(mmrp, mupars, spars, kpars)</div></code></pre>

<h4>Arguments</h4>
<dl class="rd-dl">
  <dt>(mmrp, </dt>
  <dd class="rd-dd">mupars, spars, kpars) parameters returned by pearson_bayes. mupars, spars, kpars are the ensemble of param$estimate</dd>
</dl>

  <h4>Value</h4>

  <p class="rd-p"><dl>
param Estimated parameters and standard error returned as a list($estimate, $se)
</dl></p>








## gev_bayes

<a id="gev_bayes_alias"></a><h3>Fitting the GEV distribution with Bayesian inference</h3>

<p class="rd-p">Function to fit the GEV distribution with BayesianMCMC method
WE assume that the shape parameter only has a prior with mean zero and standard deviation 0.2 (dnorm(x[3], 0, 0.2))</p>

<h4>Usage</h4>
<pre class="r"><code><div>gev_bayes(dat)</div></code></pre>

<h4>Arguments</h4>
<dl class="rd-dl">
  <dt>dat</dt>
  <dd class="rd-dd">the data that needs fitting (i.e. flood data)</dd>
</dl>

  <h4>Value</h4>

  <p class="rd-p"><dl>
param Estimated parameters and standard error returned as a list($estimate, $se)
</dl></p>



<h4>Examples</h4>
```{r gev_bayes_id_9, eval = TRUE }
library(FlomKart)
estimate = gev_bayes(test_data)
plot_density(test_data, param = estimate, distr = "gev")

```





## gev_Lmom

<a id="gev_Lmom_alias"></a><h3>Fitting the GEV distribution with Lmom</h3>

<p class="rd-p">Function to fit the GEV distribution with the linear moment method</p>

<h4>Usage</h4>
<pre class="r"><code><div>gev_Lmom(dat)</div></code></pre>

<h4>Arguments</h4>
<dl class="rd-dl">
  <dt>dat</dt>
  <dd class="rd-dd">the data that needs fitting (i.e. flood data)</dd>
</dl>

  <h4>Value</h4>

  <p class="rd-p"><dl>
param Estimated parameters and standard error returned as a list($estimate, $se).
Standard error is not yet implemented
</dl></p>



<h4>Examples</h4>
```{r gev_Lmom_id_10, eval = TRUE }
library(FlomKart)
estimate = gev_Lmom(test_data)
plot_density(test_data, param = estimate, distr = "gev")

```

<h4>See also</h4>

<a href=#gev_mle>gev_mle</a>, <a href=#gev_mom>gev_mom</a>






## gev_mle

<a id="gev_mle_alias"></a><h3>Fitting the GEV distribution with MLE</h3>

<p class="rd-p">Function to fit the GEV distribution with the maximum likelihood method</p>

<h4>Usage</h4>
<pre class="r"><code><div>gev_mle(dat)</div></code></pre>

<h4>Arguments</h4>
<dl class="rd-dl">
  <dt>dat</dt>
  <dd class="rd-dd">the data that needs fitting (i.e. flood data)</dd>
</dl>

  <h4>Value</h4>

  <p class="rd-p"><dl>
param Estimated parameters and standard error returned as a list($estimate, $se)
</dl></p>



<h4>Examples</h4>
```{r gev_mle_id_11, eval = TRUE }
library(FlomKart)
estimate = gev_mle(test_data)
plot_density(test_data, param = estimate, distr = "gev")

```

<h4>See also</h4>

<a href=#gev_lmom>gev_Lmom</a>, <a href=#gev_mom>gev_mom</a>






## gev_mom

<a id="gev_mom_alias"></a><h3>Fitting the GEV distribution with mom</h3>

<p class="rd-p">Function to fit the GEV distribution with the ordinary moments method</p>

<h4>Usage</h4>
<pre class="r"><code><div>gev_mom(dat)</div></code></pre>

<h4>Arguments</h4>
<dl class="rd-dl">
  <dt>dat</dt>
  <dd class="rd-dd">the data that needs fitting (i.e. flood data)</dd>
</dl>

  <h4>Value</h4>

  <p class="rd-p"><dl>
param Estimated parameters and standard error returned as a list($estimate, $se)
Standard error is not yet implemented
</dl></p>



<h4>Examples</h4>
```{r gev_mom_id_12, eval = TRUE }
library(FlomKart)
estimate = gev_mom(test_data)
plot_density(test_data, param = estimate, distr = "gev")

```

<h4>See also</h4>

<a href=#gev_lmom>gev_Lmom</a>, <a href=#gev_mle>gev_mle</a>






## gl_bayes

<a id="gl_bayes_alias"></a><h3>Fitting the GL distribution with Bayesian inference</h3>

<p class="rd-p">Function to fit the Generalized Logistics distribution with BayesianMCMC method
We assume that the shape parameter only has a prior with mean zero and standard deviation 0.2 (dnorm(x[3], 0, 0.2))</p>

<h4>Usage</h4>
<pre class="r"><code><div>gl_bayes(dat)</div></code></pre>

<h4>Arguments</h4>
<dl class="rd-dl">
  <dt>dat</dt>
  <dd class="rd-dd">the data that needs fitting (i.e. flood data)</dd>
</dl>

  <h4>Value</h4>

  <p class="rd-p"><dl>
param Estimated parameters and standard error returned as a list($estimate, $se)
</dl></p>



<h4>Examples</h4>
```{r gl_bayes_id_13, eval = TRUE, error=TRUE}
library(FlomKart)
estimate = gl_bayes(test_data)
plot_density(test_data, param = estimate, distr = "gl")

```





## gl_Lmom

<a id="gl_Lmom_alias"></a><h3>Fitting the GL distribution with Lmom</h3>

<p class="rd-p">Function to fit the Generalized Logistics distribution with the linear moments method</p>

<h4>Usage</h4>
<pre class="r"><code><div>gl_Lmom(dat)</div></code></pre>

<h4>Arguments</h4>
<dl class="rd-dl">
  <dt>dat</dt>
  <dd class="rd-dd">the data that needs fitting (i.e. flood data)</dd>
</dl>

  <h4>Value</h4>

  <p class="rd-p"><dl>
param Estimated parameters and standard error returned as a list($estimate, $se)
</dl></p>



<h4>Examples</h4>
```{r gl_Lmom_id_14, eval = TRUE, error=TRUE }
library(FlomKart)
estimate = gl_Lmom(test_data)
plot_density(test_data, param = estimate, distr = "gl")

```





## gl_mle

<a id="gl_mle_alias"></a><h3>Fitting the GL distribution with MLE</h3>

<p class="rd-p">Function to fit the GL distribution with the maximum likelihood method.
This function was copied from Kolbjorn's initial file</p>

<h4>Usage</h4>
<pre class="r"><code><div>gl_mle(xdat, ydat&nbsp;=&nbsp;NULL, mul&nbsp;=&nbsp;NULL, sigl&nbsp;=&nbsp;NULL, shl&nbsp;=&nbsp;NULL, mulink&nbsp;=&nbsp;identity, siglink&nbsp;=&nbsp;identity, shlink&nbsp;=&nbsp;identity, muinit&nbsp;=&nbsp;NULL, siginit&nbsp;=&nbsp;NULL, shinit&nbsp;=&nbsp;NULL, show&nbsp;=&nbsp;TRUE, method&nbsp;=&nbsp;"Nelder-Mead", maxit&nbsp;=&nbsp;10000, ...)</div></code></pre>

<h4>Arguments</h4>
<dl class="rd-dl">
  <dt>...</dt>
  <dd class="rd-dd">Function to fit the GL distribution with the maximum likelihood method.
This function was copied from Kolbjorn's initial file</dd>
</dl>

  <h4>Value</h4>

  <p class="rd-p"><dl>
param Estimated parameters and standard error returned as a list($estimate, $se)
Standard error is not yet implemented
</dl></p>



<h4>Examples</h4>
```{r gl_mle_id_15, eval = TRUE, error=TRUE }
library(FlomKart)
estimate = gl_mle(test_data)
plot_density(test_data, param = estimate, distr = "gl")

```





## gl_mom

<a id="gl_mom_alias"></a><h3>Fitting the GL distribution with mom</h3>

<p class="rd-p">Function to fit the Generalized Logistics distribution with the ordinary moments method</p>

<h4>Usage</h4>
<pre class="r"><code><div>gl_mom(dat)</div></code></pre>

<h4>Arguments</h4>
<dl class="rd-dl">
  <dt>dat</dt>
  <dd class="rd-dd">the data that needs fitting (i.e. flood data)</dd>
</dl>

  <h4>Value</h4>

  <p class="rd-p"><dl>
param Estimated parameters and standard error returned as a list($estimate, $se).
Standard error is not yet implemented
</dl></p>



<h4>Examples</h4>
```{r gl_mom_id_16, eval = TRUE, error=TRUE }
library(FlomKart)
estimate = gl_mom(test_data)
plot_density(test_data, param = estimate, distr = "gl")

```





## gumbel_bayes

<a id="gumbel_bayes_alias"></a><h3>Fitting the Gumbel distribution with Bayesian inference</h3>

<p class="rd-p">Function to fit the Gumbel distribution with BayesianMCMC method
We do not provide a prior for the BayesianMCMC function</p>

<h4>Usage</h4>
<pre class="r"><code><div>gumbel_bayes(dat)</div></code></pre>

<h4>Arguments</h4>
<dl class="rd-dl">
  <dt>dat</dt>
  <dd class="rd-dd">the data that needs fitting (i.e. flood data)</dd>
</dl>

  <h4>Value</h4>

  <p class="rd-p"><dl>
param Estimated parameters and standard error returned as a list($estimate, $se)
</dl></p>



<h4>Examples</h4>
```{r gumbel_bayes_id_17, eval = TRUE, error=TRUE }
library(FlomKart)
estimate = gumbel_bayes(test_data)
plot_density(test_data, param = estimate, distr = "gumbel")

```





## gumbel_Lmom

<a id="gumbel_Lmom_alias"></a><h3>Fitting the Gumbel distribution with Lmom</h3>

<p class="rd-p">Function to fit the Gumbel distribution with the linear moment method</p>

<h4>Usage</h4>
<pre class="r"><code><div>gumbel_Lmom(dat)</div></code></pre>

<h4>Arguments</h4>
<dl class="rd-dl">
  <dt>dat</dt>
  <dd class="rd-dd">the data that needs fitting (i.e. flood data)</dd>
</dl>

  <h4>Value</h4>

  <p class="rd-p"><dl>
param Estimated parameters (2) and standard error returned as a list($estimate, $se)
</dl></p>



<h4>Examples</h4>
```{r gumbel_Lmom_id_18, eval = TRUE, error=TRUE }
library(FlomKart)
estimate = gumbel_Lmom(test_data)
plot_density(test_data, param = estimate, distr = "gumbel")

```





## gumbel_mle

<a id="gumbel_mle_alias"></a><h3>Fitting the Gumbel distribution with MLE</h3>

<p class="rd-p">Function to fit the Gumbel distribution with the maximum likelihood method</p>

<h4>Usage</h4>
<pre class="r"><code><div>gumbel_mle(dat)</div></code></pre>

<h4>Arguments</h4>
<dl class="rd-dl">
  <dt>dat</dt>
  <dd class="rd-dd">the data that needs fitting (i.e. flood data)</dd>
</dl>

  <h4>Value</h4>

  <p class="rd-p"><dl>
param Estimated parameters (2) and standard error returned as a list($estimate, $se)
</dl></p>



<h4>Examples</h4>
```{r gumbel_mle_id_19, eval = TRUE, error=TRUE }
library(FlomKart)
estimate = gumbel_mle(test_data)
plot_density(test_data, param = estimate, distr = "gumbel")

```





## gumbel_mom

<a id="gumbel_mom_alias"></a><h3>Fitting the Gumbel distribution with mom</h3>

<p class="rd-p">Function to fit the Gumbel distribution with the ordinary moments method</p>

<h4>Usage</h4>
<pre class="r"><code><div>gumbel_mom(dat)</div></code></pre>

<h4>Arguments</h4>
<dl class="rd-dl">
  <dt>dat</dt>
  <dd class="rd-dd">the data that needs fitting (i.e. flood data)</dd>
</dl>

  <h4>Value</h4>

  <p class="rd-p"><dl>
param Estimated parameters (2) and standard error returned as a list($estimate, $se)
</dl></p>



<h4>Examples</h4>
```{r gumbel_mom_id_20, eval = TRUE, error=TRUE }
library(FlomKart)
estimate = gumbel_mom(test_data)
plot_density(test_data, param = estimate, distr = "gumbel")

```





## pearson_bayes

<a id="pearson_bayes_alias"></a><h3>Fitting the pearson distribution with Bayesian inference</h3>

<p class="rd-p">Function to fit the pearson distribution with BayesianMCMC method
WE assume that the shape parameter only has a prior with mean zero and standard deviation 0.2 (dnorm(x[3], 0, 0.2))</p>

<h4>Usage</h4>
<pre class="r"><code><div>pearson_bayes(dat)</div></code></pre>

<h4>Arguments</h4>
<dl class="rd-dl">
  <dt>dat</dt>
  <dd class="rd-dd">the data that needs fitting (i.e. flood data)</dd>
</dl>

  <h4>Value</h4>

  <p class="rd-p"><dl>
param Estimated parameters and standard error returned as a list($estimate, $se)
</dl></p>



<h4>Examples</h4>
```{r pearson_bayes_id_21, eval = TRUE, error=TRUE }
library(FlomKart)
estimate = pearson_bayes(test_data)
plot_density(test_data, param = estimate, distr = "pearson")

```





## pearson_Lmom

<a id="pearson_Lmom_alias"></a><h3>Fitting the pearson distribution with Lmom</h3>

<p class="rd-p">Function to fit the pearson distribution with the linear moment method</p>

<h4>Usage</h4>
<pre class="r"><code><div>pearson_Lmom(dat)</div></code></pre>

<h4>Arguments</h4>
<dl class="rd-dl">
  <dt>dat</dt>
  <dd class="rd-dd">the data that needs fitting (i.e. flood data)</dd>
</dl>

  <h4>Value</h4>

  <p class="rd-p"><dl>
param Estimated parameters and standard error returned as a list($estimate, $se).
Standard error is not yet implemented
</dl></p>



<h4>Examples</h4>
```{r pearson_Lmom_id_22, eval = TRUE, error=TRUE }
library(FlomKart)
estimate = pearson_Lmom(test_data)
plot_density(test_data, param = estimate, distr = "pearson")

```





## pearson_mle

<a id="pearson_mle_alias"></a><h3>Fitting the pearson distribution with MLE</h3>

<p class="rd-p">Function to fit the pearson distribution with the maximum likelihood method</p>

<h4>Usage</h4>
<pre class="r"><code><div>pearson_mle(dat)</div></code></pre>

<h4>Arguments</h4>
<dl class="rd-dl">
  <dt>dat</dt>
  <dd class="rd-dd">the data that needs fitting (i.e. flood data)</dd>
</dl>

  <h4>Value</h4>

  <p class="rd-p"><dl>
param Estimated parameters and standard error returned as a list($estimate, $se)
</dl></p>



<h4>Examples</h4>
```{r pearson_mle_id_23, eval = TRUE, error=TRUE }
library(FlomKart)
estimate = pearson_mle(test_data)
plot_density(test_data, param = estimate, distr = "pearson")

```





## pearson_mom

<a id="pearson_mom_alias"></a><h3>Fitting the pearson distribution with mom</h3>

<p class="rd-p">Function to fit the pearson distribution with the ordinary moments method</p>

<h4>Usage</h4>
<pre class="r"><code><div>pearson_mom(dat)</div></code></pre>

<h4>Arguments</h4>
<dl class="rd-dl">
  <dt>dat</dt>
  <dd class="rd-dd">the data that needs fitting (i.e. flood data)</dd>
</dl>

  <h4>Value</h4>

  <p class="rd-p"><dl>
param Estimated parameters and standard error returned as a list($estimate, $se)
Standard error is not yet implemented
</dl></p>



<h4>Examples</h4>
```{r pearson_mom_id_24, eval = TRUE, error=TRUE }
library(FlomKart)
estimate = pearson_mom(test_data)
plot_density(test_data, param = estimate, distr = "pearson")

```

